Kindly Bent to Free Us

### 2019-07-11 kindly/sdtyping/extra.tex

Furthermore, we define a term rewriting system as a system where, for every
types $\tau$,$\tau'$, there exists an equality predicates $\Ceq{\tau}{\tau'}$
which is reflexive, transitive, stable under substitution and such that,
for any predicate $P$:
\begin{align*}
  \entail{\Ceq{x}{y}\wedge \Cproj{x}C \wedge \Ceq{x}{y}&}{C}
  &\subst{x}{\tau}{P} &\equivC \Cproj{x}P \wedge \Ceq{x}{\tau}
                        \text{ where } x\notin\fv{\tau}
\end{align*}
$\CL$ is defined as the smallest cylindric term constraint system that
satisfies the axiom shown in \cref{rules:entail}.
We define  $\Ceq{\tau}{\tau'}$ as $\Cleq{\tau}{\tau'} \wedge \Cleq{\tau'}{\tau}$.
%
\begin{figure}[!b]
  \centering
  \begin{align*}
    C &::= \Cleq{\tau_1}{\tau_2}
        \mid \Cleq{k_1}{k_2}
        \mid C_1 \Cand C_2
        \mid \Cproj{\tvar}{C}
        \mid \Cproj{\kvar}{C}
  \end{align*}
  \caption{The constraint language}
  \label{grammar:constraint}
  % \input{infer/lattice}
  % \caption{Lattice inequalities -- $k \lk_\Lat k'$}
  \input{infer/entails}
  \caption{Base entailment rules -- $\entail{C}{D}$ }
  \label{rules:entail}
\end{figure}
%
We note $\SC$ the set of solved forms
which can be used inside type and kind schemes.
We define $\SC$ as $\CL$ quotiented by the relation $\equivC$.
%
The normalization function is described in \cref{infer:solving}.

% We consider the existence of a function $\operatorname{normalize}$ which takes
% a constraint in $\A$ and a substitution $\psi$ and returns a constraint
% in solved form $C' \in \SC$,
% and an updated substitution. We detail the implementation
% of the normalization function in \cref{infer:solving}

% $\mathcal S$ is composed only of kind
% inequalities \emph{over variables}. For convenience, if $C\in\mathcal S$, we
% note $C$ as a list of kind inequalities: $\Cleq{\kvar_i}{\kvar_{i'}}^n$.
% \TODO{Extend the properties of solved forms}

>>>>

Furthermore, we define a term rewriting system as a system where, for every
types $\tau$,$\tau'$, there exists an equality predicates $\Ceq{\tau}{\tau'}$
which is symmetric, reflexive, transitive, stable under substitution and such that,
for any predicate $P$:
\begin{align*}
  \entail{\Ceq{x}{y}\wedge \Cproj{x}C \wedge \Ceq{x}{y}&}{C}
  &\subst{x}{\tau}{P} &\equivC \Cproj{x}P \wedge \Ceq{x}{\tau}
                        \text{ where } x\notin\fv{\tau}
\end{align*}
$\CL$ is defined as the smallest cylindric term constraint system that
satisfies the axiom shown in \cref{rules:entail}.
We define  $\Ceq{\tau}{\tau'}$ as $\Cleq{\tau}{\tau'} \wedge \Cleq{\tau'}{\tau}$.
%
We note $\SC$ the set of solved forms
which can be used inside type and kind schemes.
We define $\SC$ as $\CL$ quotiented by the relation $\equivC$.
%
The normalization function is described in \cref{infer:solving}.
%
\begin{figure}[!hb]
  \centering
  \begin{align*}
    C &::= \Cleq{\tau_1}{\tau_2}
        \mid \Cleq{k_1}{k_2}
        \mid C_1 \Cand C_2
        \mid \Cproj{\tvar}{C}
        \mid \Cproj{\kvar}{C}
  \end{align*}
  \caption{The constraint language}
  \label{grammar:constraint}
  % \input{infer/lattice}
  % \caption{Lattice inequalities -- $k \lk_\Lat k'$}
  \input{infer/entails}
  \caption{Base entailment rules -- $\entail{C}{D}$ }
  \label{rules:entail}
\end{figure}

\subsection{Example of constraint solving and simplification}
\label{solving:example}

\input{infer/exampleconstr}

\subsection{Principal constraint system}
